\documentclass{article}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mdwlist}
\usepackage{kotex}
\usepackage[colorlinks=true]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\geometry{headheight=2in}
\geometry{top=1.0in}
\usepackage{palatino}
\usepackage{ulem}
\usepackage[parfill]{parskip}
%\renewcommand{\rmdefault}{palatino}
\usepackage{fancyhdr}
\input{../langListingMonokai}
%\pagestyle{fancy}

\newcommand{\infint}{\int_{-\infty}^{\infty}}
\newcommand{\Ab}{\bm{A}}
\rhead{}
\lhead{}
\chead{%
  {\vbox{%
      \vspace{1mm}
      \large
      Python practice 2.5\hfill \\
    }
  }
}

\usepackage{paralist}

\usepackage{todonotes}
\setlength{\marginparwidth}{2.15cm}

\usepackage{tikz}
\usetikzlibrary{positioning,shapes,backgrounds}

\newenvironment{enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\begin{document}
\thispagestyle{fancy}
\setcounter{section}{-1}

%% Q1
\section{Look and say sequence}
  Print the $N^{th}$ look and say sequence, a.k.a ant sequence.\\
  1, 11, 12, 1121, 122111....
  The sequence goes like this:\\
  1$\rightarrow$11(1이 
  1개)$\rightarrow$12(1이 2개)$\rightarrow$1121(1이 1개, 2가 1개)$\rightarrow$122111(1이 2개, 2가 1개, 1이 1개)\\
\textit{EXAMPLE}:
\begin{lstlisting}
3
12
\end{lstlisting}
%\noindent\rule{\textwidth}{0.9pt}

%% Q2
\section{Prime?}
Given input $N$($2\le N \le 10,000,000,000$), Print 'True' if $N$ is a prime number. Print 'False' otherwise. 
\textit{EXAMPLE}:
\begin{lstlisting}
1217
True
\end{lstlisting}

%% Q3
\section{Wrd Shrtnr}
Given input, remove vowels(\textit{a,e,i,o,u}).\\
\textit{EXAMPLE}:
\begin{lstlisting}
chicken
chckn
\end{lstlisting}

%% Q4
\section{Digit Counter}
Given N, print the occurrence of each digit without using the Counter
class.(The answer is similar to how Counter works)\\
\textit{EXAMPLE}:
\begin{lstlisting}
12353
0:0
1:1
2:1
3:2
4:0
5:1
6:0
7:0
8:0
9:0
\end{lstlisting}

\section{Where are you?}
We can easily get the maximum value of a list by $max(lst)$.\\
But finding its index is not as easy. Write a program that prints the index of
the maximum value. (Note that the index starts from 0).
\begin{lstlisting}
10 3 5 100 9
3
\end{lstlisting}

\section{Genetic Algorithm}
Genetic Algorithm is an optimization technique that mimics the process of
evolution and natural selection. This time, we are going to find the largest
number in between ($0_{(2)}, 1111111111_{(2)}$) using GA. The answer
is obviously $1111111111_{(2)}$, but lets see if natural selection can figure that out.
Please fill in the $TODO$s. Reading this link would help:
\href{https://namu.wiki/w/유전알고리즘}{유전알고리즘}.\\
Download "genetic\_skelton.py" to start.

\end{document}
