\documentclass{article}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mdwlist}
\usepackage[colorlinks=true]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\geometry{headheight=2in}
\geometry{top=1.0in}
\usepackage{palatino}
\usepackage{ulem}
\usepackage[parfill]{parskip}
%\renewcommand{\rmdefault}{palatino}
\usepackage{fancyhdr}
\input{../langListingMonokai}
%\pagestyle{fancy}

\newcommand{\infint}{\int_{-\infty}^{\infty}}
\newcommand{\Ab}{\bm{A}}
\rhead{}
\lhead{}
\chead{%
  {\vbox{%
      \vspace{1mm}
      \large
      Python practice 2\hfill \\
    }
  }
}

\usepackage{paralist}

\usepackage{todonotes}
\setlength{\marginparwidth}{2.15cm}

\usepackage{tikz}
\usetikzlibrary{positioning,shapes,backgrounds}

\newenvironment{enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\begin{document}
\thispagestyle{fancy}
\setcounter{section}{-1}

%% Q1
\section{DIE with a T}
I am on a diet. So I can only eat upto 2,000 kcal (2,000,000 cal) a day.
I eat 4 meals a day(\textit{b}reakfast, \textit{l}unch, \textit{s}nack, and
\textit{d}inner) and life would be easy if
every food was exactly 500,000cal. But it isn't. So help me out.
From 4 different groups of foods(each group representing the 4 meals I eat) each consisting of $N$ foods, compute whether it is possible to select a food from each group
so that the total calorie intake is \textit{exactly} 2,000,000 cal.\\
\noindent\rule{\textwidth}{0.9pt}
\textit{INPUT}: The first line is integer $N$.
The \textit{i}-th line of next $N$ lines contains the four calorie value of each
meal, $b_{i}, l_{i}, s_{i}, d_{i}$.

\textit{OUTPUT}: Print \textbf{SUCCESS} if we can choose exactly 4 food so that
the total of calorie equals 2,000,000.\\($b_{i}+l_{i}+s_{i}+d_{i} = 2,000,000$)
Print \textbf{FAIL} elsewise.

\textit{CONDITION}: $ 4 \le N \le 10,000$, $ 0 \le b,l,s,d \le 1,000,000$

\textit{EXAMPLE}:
\begin{lstlisting}
2
100000 600000 400000 600000
200000 500000 600000 800000
\end{lstlisting}
\begin{lstlisting}
SUCCESS
\end{lstlisting}
\begin{lstlisting}
1
100000 600000 400000 600000
\end{lstlisting}
\begin{lstlisting}
FAIL
\end{lstlisting}

\textit{HINT}: The obvious approach would be to try every combination
of $4$ foods from each meal. However, this approach takes time proportional to $N^4$,
which is $10000000000000000$ in the worst case.
Therefore, instead of trying every combination, we need a better approach.
One possible approach would be computing \textit{partial} calorie $k$ in time
proportional to $N^2$, and checking whether $(2000000-k)$ exists in $constant$ time. This can be done by a $set$. Using a $set$ also has the added benefit of
removing duplicates, reducing computation time somewhat.\\
\noindent\rule{\textwidth}{0.9pt}

%% Q2
\section{Statistics Showdown}
Given $N$($N \% 2 == 1$) numbers, compute the following representative values.
\begin{enumerate}
  \item Arithmetic Mean
  \item Geometric Mean
  \item Median
  \item Mode (The most common value)
  \item Range ($max(n_i) - min(n_i)$)
\end{enumerate}

\noindent\rule{\textwidth}{0.9pt}
\textit{INPUT}: The first line is integer $N$.
The \textit{i}-th line of next $N$ lines contains a single integer $n_{i}$.

\textit{OUTPUT}: Print 5 lines, each consisting of the Arithmetic Mean, Geometric
Mean, Median, Mode, and Range of $n_{i}$. If there are more than 1 mode, print
any of those. For Arithmetic and Geometric mean,
round to one decimal place (\textit{e.g.} $1.75 = 1.8, 3.74 = 3.7$).

\textit{CONDITION}: $ 1 \le N \le 200$ ($N$ is odd number),  $ 0 \le n_{i} \le 1000$

\textit{EXAMPLE}:
\begin{lstlisting}
5
1
4
2
3
5
\end{lstlisting}

\begin{lstlisting}
3.0
2.6
3
1
4
\end{lstlisting}

\textit{HINT}: Googling "root in python (other than square root)" would help
calculating the Geometric Mean.
\noindent\rule{\textwidth}{0.9pt}

%% Q3
\section{Prefix Calculator}
We usually write mathematical expressions this way:
$3+4*2$. This is called an infix notation, and although easy to understand, it has
some drawbacks.
%\begin{enumerate}
  %\item We have to know precedence rules of operators to correctly compute the
    %expression. Without knowing that '*' comes before '+', $3+4*2$ can be
    %miscalculated as $14$.
  %\item We have to use parentheses to express the intended order of operations.
    %$(3+4)*2$ if we want the result to be 14.
%\end{enumerate}
Therefore, there are other notations like prefix notations(operators precede
their operands), or postfix notations(operators follow their operands).
For example, using prefix notation, the expression above becomes $(+\ 3\ (*\ 4\
2))$.
To evaluate this expression, we start from the left, and when we see an
operator('+'), we expect two sub-expressions. We see a 3 and (* 4 2).
3 is 3. For (* 4 2), we repeat the step above, with an operator('*') and
two sub-expressions (4 and 2). Since there are no more sub-expressions to be
evaluated, we calculate $(*\ 4\ 2) = 8$, and $(+\ 3\ 8) = 11$.

TLDR; we are going to implement a mathematical expression calculator.
For your convenience, I have already implemented the $infix\_prefix(exp)$
(There is no need to understand how it works).
It's your job fill in $calculate(exp)$ that evaluates the prefix notation,
\textit{recursively}.


\noindent\rule{\textwidth}{0.9pt}
\textit{INPUT}: A single line of a correct mathematical expression, with
parentheses.

\textit{OUTPUT}: The result of calculating the mathematical expression.

\textit{CONDITION}: For simplicity, the numbers used in the expression is a
single digit number, ranging from 0 to 9. The operators used are $+(addition),
-(substraction), *(multiplication), /(division)$.

\textit{EXAMPLE}:
\begin{lstlisting}
(3+2)*2
10
\end{lstlisting}

\textit{HINT}: Before implementing calculate(prefix\_exp), examine the prefix notation
of expressions. We can see that the prefix expression is formed as following:
\begin{alignat*}{3}
  prefix\_exp &::= \ \  &&(operand,\ prefix\_exp,\ prefix\_exp)\ \  &&tuple\\
      &\ \ \ | &&n &&integer
\end{alignat*}
When the type of the prefix\_exp is integer, (in Python:
$isinstance(prefix\_exp,\ int)$), there
is nothing to do; return $n$. This becomes the basecase
of recursion. When it's a tuple, we have to do some calculation. Assuming that
$calculate(prefix\_exp)$ will correctly calculate the results of the two subexpression would help.\\
\noindent\rule{\textwidth}{0.9pt}

%% Q4
\section{Heart Signal}
It is not often the case that someone you love, loves you back. It was easily
observed in the heartwarming(or breaking?) tvshow Heart Signal. Now, as a fan
of the show, it is of our interest to see if the participants can fulfill their love.
Meaning that, someone who the participant likes also likes the participant
back.\\
\noindent\rule{\textwidth}{0.9pt}
\textit{INPUT}: The first line is integer $N$. The \textit{i}-th line of next
$N$ lines contains the participant's name, and the someone he/she likes,
seperated by a space. The \textit{N+2}-th(last) line contains the name of a
participant. 

\textit{OUTPUT}: If the participant is also liked by the someone he/she likes,
print \textbf{LOVE}. print \break{OUCH} elsewise.

\textit{EXAMPLE}:
\begin{lstlisting}
5
hulk blackwidow
hawkeye blackwidow
blackwidow ironman
ironman pepper
pepper ironman
hulk

OUCH
\end{lstlisting}

\begin{lstlisting}
6
hulk blackwidow
hawkeye blackwidow
blackwidow ironman
ironman pepper
pepper ironman
pepper

LOVE
\end{lstlisting}
\textit{HINT}: We would be using a list if the names were just integers...
\noindent\rule{\textwidth}{0.9pt}

\end{document}
